---
title: Supplementary Tables - working draft
output:
   word_document:
    reference_docx: "word_styles_prelim_report.docx"

---

```{r, eval=FALSE, echo=FALSE}
rmarkdown::render(input = 'R/Supplementary_Tables.Rmd', output_dir = "drafts")
```


**Table S1.** Summary of the number of studies of different types (mesocosm or field), 
experimental approaches (laboratory, greenhouse, outdoor, experiment, or observation) 
and predictor variability for the metric of eelgrass (*Zostera marina*) performance recorded. 
Predictor variability refers to whether variation in light or temperature values 
across experiments could be measured (= Variable) or had to be assumed to be constant 
(see Fig. S1). The number of unique study-site-treatment combinations is given in parentheses.

```{r, echo=FALSE}
methods_table <- readRDS('../data_outputs/methods_table.RDS')
methods_table
```

<br>

**Table S2.** Catchall table for quick and updateable values that can be noted in 
the results description of data section. Will most likely be removed or at least
restructured

```{r, echo=FALSE}
data_description_table <- readRDS("../data_outputs/data_description_table.RDS")
data_description_table
```